Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-07-28 writeup/conStruct.tex
G's structure comparison

>>>>

A nice feature of our approach is that our model contains a non-spatial assignment model as a special case. 
Setting $\alpha_0^{(k)}$ to zero for all $k$, we obtain a non-spatial model where
each cluster has its own allele frequency at each SNP, and individuals
draw a proportion of their ancestry from each cluster. This model is
strongly conceptually similar to that of STRUCTURE (and related
approaches ADMIXTURE), the only difference being that our likelihood
assumes that allele frequencies are normally distributed around their
expectations, while the standard assignment methods assume that the
error is binomial distributed (see XXXX). Therefore, to compare the fit
of
